Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-06-07 assets/scatter_model.tex
:paintbrush: Update plots

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\large]
	\draw (0,0) node[bareantenna](bareantenna){};
	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3.5,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E1);
	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E2);
	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E3);
	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) coordinate(E4);
	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
	\draw (E1) to[short,-*] (E2);
	\draw (E2) to[short,-*] (E3);
	% \draw (E2) to[short,-*] (E);
	% \draw (E) to[short,-*] (E3);
	\draw (E3) to[short] (E4);
	\draw (E2) to[short] ++(1,0) node[ground]{};
\end{circuitikz}

>>>>

\begin{circuitikz}[transform shape]
	\tikzstyle{every node}=[font=\large]
	\draw (0,0) node[bareantenna](bareantenna){};
	\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\mathrm{I}}$};
	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\mathrm{I}}$};
	\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
	\draw (bareantenna) to ++(0,-1.5) to [generic,l=$Z_{\mathrm{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E1);
	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E2);
	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E3);
	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.5,0) coordinate(E4);
	% \coordinate (E) at ($(E2)! 0.5!(E3)$);
	\draw (E1) to[short,-*] (E2);
	\draw (E2) to[short,-*] (E3);
	% \draw (E2) to[short,-*] (E);
	% \draw (E) to[short,-*] (E3);
	\draw (E3) to[short] (E4);
	\draw (E2) to[short] ++(0.5,0) node[ground,rotate=90]{};
\end{circuitikz}

### 2022-06-07 main.tex
:paintbrush: Update plots

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes primary link.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional backscatter paths to transmit and assist.
	% the \gls{kkt} input distribution is

	% KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate

	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
	% the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	% Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	% Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	% We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

>>>>

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional backscatter paths to coordinate transmit and assist via smart input design.
\end{abstract}
